Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
"wavelet scalogram" -> "scalogram" in two places

The wavelet transform of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelet filters
Applying pointwise complex modulus the transform yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t)\mbox{.}
\end{equation}
The scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q_1}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the temporal resolution of the traditional CQT is fixed by the support of the STFT analyzing window. %\cite{Brown1992}
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost
since the inverse fast Fourier transform (IFFT) routine must be called for each wavelet $\boldsymbol{\psi_{\gamma_1}}$ in the filter bank. \ja{Is the cost really greater?}
However, this allows us to observe amplitude modulations at fine temporal scales in the scalogram, down to $2Q_1/\xi_1$ for $\gamma_1 = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$. \ja{Where does the formula $2Q_1/\xi_1$ come from?}

>>>>

The wavelet transform of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelet filters
Applying pointwise complex modulus the transform yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t)\mbox{.}
\end{equation}
The scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q_1}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the temporal resolution of the traditional CQT is fixed by the support of the STFT analyzing window. %\cite{Brown1992}
Therefore, the scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost
since the inverse fast Fourier transform (IFFT) routine must be called for each wavelet $\boldsymbol{\psi_{\gamma_1}}$ in the filter bank. \ja{Is the cost really greater?}
However, this allows us to observe amplitude modulations at fine temporal scales in the scalogram, down to $2Q_1/\xi_1$ for $\gamma_1 = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$. \ja{Where does the formula $2Q_1/\xi_1$ come from?}
